InteroceptionStudy_GPValidation

### 2021-08-20 Experiment 2.Rmd
Update Experiment 2.Rmd

# gsr for leda
colnames(tmp.df3)
db_GSR<- select(tmp.df3, c(3,  14, 17, 50, 49 ))
db_GSR$tNo<- NULL
colnames(db_GSR)

@@

@@

tmp.df3<- tmp.df3%>%
  arrange(ssid, tNo,time)%>%
  group_by(ssid, tNo, gsr_bastrue)%>%
  mutate(gsr_bas_median = median(gsr_bas))

@@

# note that smothing and interpolating is order dependednt so order by ssid, trial and time
tmp.df3<- tmp.df3 %>%
  arrange(ssid, trialUnq,tNo, time)%>%
  group_by(ssid, trialUnq,tNo,screencontent) %>%
  mutate(extendpupil=gazer::extend_blinks(pupil, fillback=100, fillforward=100, hz=150))

@@

# vert order dependent
tmp.df3 <- smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
                                    extendblinks=TRUE, step.first= 'smooth',
                                    maxgap=Inf, 
                                    filter = 'moving',
                                    type="linear", hz=150, n = 30)

@@

subset(tmp.df3, tNo == 1)%>%
ggplot(aes(x = timerezero3, y= pup_interp))+
  geom_line()+
   geom_line(aes(y = extendpupil), color = 'red')+
  # geom_line(aes(y = pup_interp), colour = 'gray')+
    facet_grid(~ssid)
  # facet_grid(~Condition)
```

@@

ggplot(subset(tmp.df3, tNo == 10 & tmp.df3$ssid == 354) , aes(x = timerezero3, y= pup_basCor))+
    # geom_smooth(se = F)+
  geom_line()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
```
unique(tmp.df3$ssid)

>>>>

# gsr for leda
colnames(tmp.df3)
db_GSR<- select(tmp.df3, c(3,  14, 17, 50, 49,51 ))
db_GSR$tNo<- NULL
colnames(db_GSR)

@@

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021")

@@

tmp.df3<- tmp.df3%>%
  arrange(ssid, time,tNo)%>%
  group_by(ssid, tNo, gsr_bastrue)%>%
  mutate(gsr_bas_median = median(gsr_bas))

@@

# note that smothing and interpolating is order dependednt so order by ssid, trial and time
tmp.df3<- tmp.df3 %>%
  arrange(ssid, time,tNo)%>%
  group_by(ssid, trialUnq,tNo,screencontent) %>%
  mutate(extendpupil=gazer::extend_blinks(pupil, fillback=100, fillforward=100, hz=150))

@@

# vert order dependent
tmp.df3 <- gazer::smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
                                    extendblinks=TRUE, step.first= 'smooth',
                                    maxgap=Inf, 
                                    filter = 'moving',
                                    type="linear", hz=150, n = 30)

@@

subset(tmp.df3, tNo == 1)%>%
ggplot(aes(x = timerezero3, y= pup_interp))+
  geom_line()+
   # geom_line(aes(y = extendpupil), color = 'red')+
  # geom_line(aes(y = pup_interp), colour = 'gray')+
    facet_grid(~ssid)
  # facet_grid(~Condition)
```

@@

ggplot(subset(tmp.df3, tNo == 10 & tmp.df3$ssid == 354) , aes(x = timerezero3, y= pup_basCor))+
    # geom_smooth(se = F)+
  geom_line()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

ggplot(subset(tmp.df3, tNo == 10 & tmp.df3$ssid == 354) , aes(x = timerezero3, y= pup_basCor))+
    # geom_smooth(se = F)+
  geom_line()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)+
  xlim(-3,3)

subset(tmp.df3, tNo == 10)%>%
  group_by(ssid, tNo)%>%
  mutate(pupil_z = pup_interp_mad - mean(pup_interp_mad))%>%
ggplot(aes(x = timerezero3, y= pupil_z))+
    # geom_smooth(se = F)+
  geom_smooth()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)+
  xlim(-6,15)
```
unique(tmp.df3$ssid)
